|

### 2019-08-27 paper.Rmd
Starting work on introduction.

A good way to visualize high-dimensional data is to display a smooth sequence of interpolated lower dimensional projections. This is called a tour [@As85; @BCAH05] and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. A limitation of this approach is that concavities in a distribution may be hidden when looking at projections. A simple example are projections of samples on a hypersphere. No projection of such a distribution allows to distinguish a hollow sphere from a full one. On the other hand, the difference would be obvious when looking at a slice through the center of the sphere.

@@

Here we propose a systematic approach to slicing that does not rely on the user choosing sections to display, but will present the viewer with an interpolated sequence showing different slices of parameter space. The method is based on the grand tour, and uses the orthogonal distance from the current plane to define the section corresponding to each view in an interpolated tour path. We demonstrate how this can be used to gain insights into the concave structure of a dataset, using the example of hollow hyperspheres defined in 3 or more dimensions.

@@

XXXX not sure this makes sense, need to check against plots (not what I was expecting, need to think about this more)

>>>>

Modern data is typically high-dimensional and thus data visualisation often relies on some form of dimension reduction. Interactive and dynamic displays provide information beyond what can be achieved in a static display. For example, the grand tour [@As85; @BCAH05] shows a smooth sequence of interpolated lower dimensional projections and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. Additionaly we may complement projections with section information. This is often possible in interactive graphics systems by means of brushing [@ggobiCSDA2003;@JSSv081i05],
(XXX check what references to put)
where the user is selecting a region in a subspace of the dataspace that is highlighted in a projection of the data points. The complementarity between projections and sectionings has previously been discussed in @prosection, dubbing the combination "prosections". These prosections were found to allow identification of lower-dimensional structure embedded in the high-dimensional space. One simple example is that prosections can reveal the difference between a full and hollow hypersphere, that is it reveals the intrinsically lower dimension of the hyper-surface embedded in the higher-dimensional space.

However, all existing approaches to sectioning are interactive and rely on the user to redefine the section many times to explore the possible sections. While this is often preferred, it is impractical for detecting and exploring unknown concave structures in a dataset. We therefore propose a more systematic approach to sectioning based on interpolated projections obtained with a grand tour. The method defines a slice based on 2-d projections provided by the tour and thus presents the user with an interpolated sequence of slices through the data space.

We first define the new slice tour in Section XXX, and outline the implementation in R in Section XXX. We then apply the method to examples from the geozoo package, showing how hollowness can be visualised and explored with a slice tour. Possible extensions are discussed in Section XXX.

<!--
A good way to visualize high-dimensional data is to display a smooth sequence of interpolated lower dimensional projections. This is called a tour [@As85; @BCAH05] and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. A limitation of this approach is that concavities in a distribution may be hidden when looking at projections. A simple example are projections of samples on a hypersphere. No projection of such a distribution allows to distinguish a hollow sphere from a full one. On the other hand, the difference would be obvious when looking at a slice through the center of the sphere.

@@

Here we propose a systematic approach to slicing that does not rely on the user choosing sections to display, but will present the viewer with an interpolated sequence showing different slices of parameter space. The method is based on the grand tour, and uses the orthogonal distance from the current plane to define the section corresponding to each view in an interpolated tour path. We demonstrate how this can be used to gain insights into the concave structure of a dataset, using the example of hollow hyperspheres defined in 3 or more dimensions.
-->

@@

XXXX not sure this makes sense, need to check against plots (not what I was expecting, need to think about this more)
Best guess is that relation between $\phi$ and $h$ only holds for 3d sphere, how can I generalise it?
